An efficient acyclic contact planner for legged robots

### 2017-01-19 body/appendix_optim.tex
cosmetics

\subsection{The centroidal cone}
We rewrite Eq.~\ref{eq:new_eul} in the general case:

@@

where $\dot{L}$ is the angular momentum expressed at the com.
Eq.~\ref{eq:new_eul} defines a 6 dimensional cone $\mathcal{K}$ ~\citep{qiu:dhm:2011,Caron2015}. For a given set of contacts,
this cone determines all the admissible wrenches $\mathbf{w}$ such that the robot won't fall. The objective 
is thus to plan a trajectory for $c$ and $\dot{L}$ that remains inside $\mathcal{K}$. As a cone,
$\mathcal{K}$ can be described as a linear inequality, obtained with the double description method~\citep{Fukuda1996}:

@@

\begin{equation} \label{eq:lin_prog_rob} \begin{aligned}
%~ \find \quad & \mx{R} \in \Rv{3\times T}, \mxdd{C} \in  \Rv{6\times T} \\
\minimize_{\mathbf{c}(t), \mathbf{w}(t)}  \quad & \sum_{s=0}^{2} \int_{t_s}^{t_s + \Delta t_s}  h(\mathbf{c}, \mathbf{w})  \\
\st \quad & \mathbf{\dot{c}} = f(\mathbf{c}, \mathbf{w}) \\
	\quad & \mathbf{A}_s \mathbf{w}(t)  \leq \mathbf{b}_s , \forall t \in  \left[t_s, t_s + \Delta t_s \right[ \\
	\quad & \mathbf{c}(0)  = \mathbf{c}_{\mathbf{q}_0} \\
	\quad & \mathbf{c}(T)  = \mathbf{c}_{\mathbf{q}_1} \\
	\quad & \mathbf{c}(0)  = \mathbf{\dot{c}}(0)  = \mathbf{\ddot{c}}(0) = \mathbf{0}\\
	\quad & \mathbf{c}(T)  = \mathbf{\dot{c}}(T)  = \mathbf{\ddot{c}}(T) = \mathbf{0}\\
    %~ \quad & ({\vct{r}}\tra\vct{r}=1,  \forall t  ?) \\
    %~ \quad & \delta t \sum\limits_1^{T-1}{\vc{r}^1}\tra {\vc{r}^1} \ge t_{transit} \\
    %~ \quad & \mx{A}_{\int} \mxdd{C} \leq \vc{a}_{\int} \\
    %~ \quad & \mx{V}_{\int} \mxd{C} \leq \vc{v}_{\int} \\
    %~ \quad & \mx{B}_{\int}^{1} \mx{C} \leq \vc{b}_{\int} \\
    %~ \quad & [\vc{c}_0\tra, \vcd{c}_0\tra]\tra = \vc{x}_0 \\
    %~ \quad & \vc{c}_T = \vc{c}_T^{input} \\
\end{aligned} \end{equation}

where $h$ is a cost function (We typically minimize the angular momentum and acceleration over the whole trajectory, and use
a log barrier to constrain kinematically the center of mass position with respect to the contact locations).
This formulation can trivially be extended over the whole contact sequence.
In our implementation, the problem is discretized using time steps of 100 ms.

>>>>

We rewrite Eq.~\ref{eq:new_eul} in the general case:

@@

where $\dot{L}$ is the angular momentum expressed at the com.
Eq.~\ref{eq:new_eul_acc} defines a 6 dimensional cone $\mathcal{K}$ ~\citep{qiu:dhm:2011,Caron2015}. For a given set of contacts,
this cone determines all the admissible wrenches $\mathbf{w}$ such that the robot won't fall. The objective 
is thus to plan a trajectory for $c$ and $\dot{L}$ that remains inside $\mathcal{K}$. As a cone,
$\mathcal{K}$ can be described as a linear inequality, obtained with the double description method~\citep{Fukuda1996}:

@@

\begin{equation} \label{eq:lin_prog_rob} \begin{aligned}
%~ \find \quad & \mx{R} \in \Rv{3\times T}, \mxdd{C} \in  \Rv{6\times T} \\
\minimize_{\mathbf{c}(t), \mathbf{w}(t)}  \quad & \sum_{s=0}^{2} \int_{t_s}^{t_s + \Delta t_s}  h(\mathbf{c}, \mathbf{w})  \\
\st \quad & \mathbf{\dot{c}} = f(\mathbf{c}, \mathbf{w}) \\
	\quad & \mathbf{A}_s \mathbf{w}(t)  \leq \mathbf{b}_s , \forall t \in  \left[t_s, t_s + \Delta t_s \right[ \\
	\quad & \mathbf{D}_s \mathbf{c}(t)  \leq \mathbf{d}_s , \forall t \in  \left[t_s, t_s + \Delta t_s \right[ \\
	\quad & \mathbf{c}(0)  = \mathbf{c}_{\mathbf{q}_0} \\
	\quad & \mathbf{c}(T)  = \mathbf{c}_{\mathbf{q}_1} \\
	\quad & \mathbf{c}(0)  = \mathbf{\dot{c}}(0)  = \mathbf{\ddot{c}}(0) = \mathbf{0}\\
	\quad & \mathbf{c}(T)  = \mathbf{\dot{c}}(T)  = \mathbf{\ddot{c}}(T) = \mathbf{0}\\
    %~ \quad & ({\vct{r}}\tra\vct{r}=1,  \forall t  ?) \\
    %~ \quad & \delta t \sum\limits_1^{T-1}{\vc{r}^1}\tra {\vc{r}^1} \ge t_{transit} \\
    %~ \quad & \mx{A}_{\int} \mxdd{C} \leq \vc{a}_{\int} \\
    %~ \quad & \mx{V}_{\int} \mxd{C} \leq \vc{v}_{\int} \\
    %~ \quad & \mx{B}_{\int}^{1} \mx{C} \leq \vc{b}_{\int} \\
    %~ \quad & [\vc{c}_0\tra, \vcd{c}_0\tra]\tra = \vc{x}_0 \\
    %~ \quad & \vc{c}_T = \vc{c}_T^{input} \\
\end{aligned} \end{equation}

$h$ is a cost function (We typically minimize the angular momentum and acceleration over the whole trajectory, and use
a log barrier to constrain kinematically the center of mass position with respect to the contact locations). $f$ is the colocation method
bounding the position, velocity and acceleration of the center of mass. 
$\mathbf{D}_s$ and $\mathbf{d}_s$ denote stacked kinematic constraints on the center of mass position, determined by the active contact locations.
The inequalities for each contact are determined in the same way that the reachable workspace is computed in Appendix~\ref{app:rom}, with
the effector serving as root (a triangulated object is a polytope, and as such can be described as a set of linear inequalities).

This formulation can trivially be extended over the whole contact sequence.
In our implementation, the problem is discretized using time steps of 100 ms.
